---
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    anchor_sections: false
---

<br>

```{r global, include=FALSE, echo=F, context="setup", results='hide'}


library(flexdashboard)
knitr::opts_chunk$set(echo = F, message = F, warning = F)

library(shiny)
library(janitor)
library(DT)
library(magrittr)
library(glue)
library(highcharter)
library(lubridate)
library(knitr)
library(tidyverse)
library(htmltools)
library(shinyWidgets)



# snap_ads <- readRDS("data/snap_ads.RDS")
# 
trans <- readRDS("../data/trans_dutch.rds")
# trans <- readRDS("../data/trans_eng.rds")
# 
# 



source("../../R/helpers.R")
source("../../R/dashboard_data.R")


map_data <- readRDS("../data/mapdata.RDS")

```



## Gender Targeting {.tabset .tabset-fade .tabset-pills}

### Facebook Platforms (incl. Instagram) {.tabset .tabset-fade .tabset-pills}


#### All at Once

```{r, out.width="100%", fig.height=15}

  fb_aggr %>%
    hc_plotter(filters = dutch_parties_fb,
           plot_type = unlist_it(trans$choices, 4),
           plot_type_sub = unlist_it(trans$targeted_ads_choices, 1),
           platform = "Facebook",
           trans_internal = trans,
           last_updated = update_time, minmax = "Minimum"
    )

```
For every ad, the Facebook ad library provides a “percentage” which relates to the share of the specific demographic that has seen the ad. So, the audience of an ad could show, for example, that 60% of the users that have seen the ad were women. This metric is calculated by taking the median of percentages for every unique ad. The boxplots show the distribution of average audience shares per demographic group by advertiser. Knowing the share of the audience that saw an ad may give us an insight into how an individual party tried to target a specific demographic group. However, this metric does not relate to "targeting" 1-to-1 because it is possible that the Facebook ad placing algorithm is more likely to show ads to people that are likely to engage with the ads in the first place thus reflecting the demographics of party supporters rather than strategy.


#### Per Party

```{r, out.width="100%", fig.height=15}


gg_gender <- fb_aggr$gender %>% 
  filter(advertiser_name %in% dutch_parties_fb)  %>% 
          filter(gender %in% c("male", "female")) %>% 
          mutate(gender = ifelse(gender == "male", trans$gender_male, trans$gender_female)) %>% 
  ggplot(aes(gender, percentage, color = gender)) +
  geom_boxplot() +
  ggthemes::scale_color_hc() +
  facet_wrap(~advertiser_name, ncol = 3, scales = "free_x") +
  ylim(0, 100) +
  theme_minimal() +
  labs(y = "", x = "") +
  theme(legend.position = "top", 
        strip.background =element_rect(fill="lightgrey"), 
        strip.text = element_text(colour = 'black'), axis.title.x = element_text(size = 0.1))


gg_gender %>% 
  plotly::ggplotly(dynamicTicks = F) %>%
  plotly::layout(
    xaxis = list(automargin=TRUE),
    yaxis = list(automargin=TRUE,
                 title = trans$plot_yaxis_gender_fb,
                 titlefont  = list(size = 0.1)),
    legend = list(
    orientation = "h",
    y = 1.05
    )
  ) 
```


For every ad, the Facebook ad library provides a “percentage” which relates to the share of the specific demographic that has seen the ad. So, the audience of an ad could show, for example, that 60% of the users that have seen the ad were women. This metric is calculated by taking the median of percentages for every unique ad. The boxplots show the distribution of average audience shares per demographic group by advertiser. Knowing the share of the audience that saw an ad may give us an insight into how an individual party tried to target a specific demographic group. However, this metric does not relate to "targeting" 1-to-1 because it is possible that the Facebook ad placing algorithm is more likely to show ads to people that are likely to engage with the ads in the first place thus reflecting the demographics of party supporters rather than strategy.



### Google Platforms (incl. YouTube)



```{r}
  ggl_aggr %>% 
    hc_plotter(filters = dutch_parties,
           plot_type = unlist_it(trans$choices, 4),
           plot_type_sub = unlist_it(trans$targeted_ads_choices, 1),
           platform = "Google",
           trans_internal = trans,
           last_updated = update_time, minmax = "Minimum"
    )
```




## Age Targeting {.tabset .tabset-fade .tabset-pills}

### Facebook Platforms (incl. Instagram) {.tabset .tabset-fade .tabset-pills}






#### All at Once

```{r}
  fb_aggr %>%
    hc_plotter(filters = dutch_parties_fb,
           plot_type = unlist_it(trans$choices, 4),
           plot_type_sub = unlist_it(trans$targeted_ads_choices, 2),
           platform = "Facebook",
           trans_internal = trans,
           last_updated = update_time, minmax = "Minimum"
    )
```

For every ad, the Facebook ad library provides a “percentage” which relates to the share of the specific demographic that has seen the ad. So, the audience of an ad could show, for example, that 60% of the users that have seen the ad were between 18-24 This metric is calculated by taking the median of percentages for every unique ad. The boxplots show the distribution of average audience shares per demographic group by advertiser. Knowing the share of the audience that saw an ad may give us an insight into how an individual party tried to target a specific demographic group. However, this metric does not relate to "targeting" 1-to-1 because it is possible that the Facebook ad placing algorithm is more likely to show ads to people that are likely to engage with the ads in the first place thus reflecting the demographics of party supporters rather than strategy.


#### Per Party

```{r, out.width="100%", fig.height=15, fig.width=10}

# debugonce(hc_plot_boxes)





gg_age <- fb_aggr$age %>% 
  filter(advertiser_name %in% dutch_parties_fb)  %>% 
  ggplot(aes(age, percentage, color = age)) +
  geom_boxplot() +
  ggthemes::scale_color_hc() +
  facet_wrap(~advertiser_name, ncol = 2, scales = "free_x") +
  ylim(0, 100) +
  theme_minimal() +
  labs(y = "", x = "") +
  theme(legend.position = "top", 
        strip.background =element_rect(fill="lightgrey"), 
        strip.text = element_text(colour = 'black'), axis.title.x = element_text(size = 0.1))


gg_age %>% 
  plotly::ggplotly(dynamicTicks = F) %>%
  plotly::layout(
    xaxis = list(automargin=TRUE),
    yaxis = list(automargin=TRUE,
                 title = trans$plot_yaxis_age_fb,
                 titlefont  = list(size = 0.1)),
    legend = list(
    orientation = "h",
    y = 1.05
    )
  ) 
```

For every ad, the Facebook ad library provides a “percentage” which relates to the share of the specific demographic that has seen the ad. So, the audience of an ad could show, for example, that 60% of the users that have seen the ad were between 18-24 This metric is calculated by taking the median of percentages for every unique ad. The boxplots show the distribution of average audience shares per demographic group by advertiser. Knowing the share of the audience that saw an ad may give us an insight into how an individual party tried to target a specific demographic group. However, this metric does not relate to "targeting" 1-to-1 because it is possible that the Facebook ad placing algorithm is more likely to show ads to people that are likely to engage with the ads in the first place thus reflecting the demographics of party supporters rather than strategy.



### Google Platforms (incl. YouTube)



```{r}
  ggl_aggr %>% 
    hc_plotter(filters = dutch_parties,
           plot_type = unlist_it(trans$choices, 4),
           plot_type_sub = unlist_it(trans$targeted_ads_choices, 2),
           platform = "Google",
           trans_internal = trans,
           last_updated = update_time, minmax = "Minimum"
    )
```

For Google platforms, the Google Transparency Report provides information about the groups that the advertiser chose to target rather than just information about the audience of an ad, like Facebook does.  This information is much more insightful as it reveals the targeting strategy set by the advertisers themselves. Per [Google]((https://support.google.com/transparencyreport/answer/9575640)), targeting for election ads is limited to "[g]eographic location (except radius around a location), age, and gender." The percentages shown relate to how many of the ads were targeted towards these specific criteria.  


## Geo Targeting {.tabset .tabset-fade .tabset-pills}

### Facebook Platforms (incl. Instagram) {.tabset .tabset-fade .tabset-pills}

```{r}
# debugonce(hc_plotter)

# fb_aggr$geo %>% filter(advertiser_name == "CDA")
  fb_aggr %>% 
    hc_plotter(filters = dutch_parties_fb,
           plot_type = unlist_it(trans$choices, 4),
           plot_type_sub = unlist_it(trans$targeted_ads_choices, 3),
           platform = "Facebook",
           mapdata = map_data,
           trans_internal = trans,
           last_updated = update_time, minmax = "Minimum"
    )
  
   # hc_data %>% 
   #   chart_maps(F, mapdata, trans) %>% hw_grid(ncol = 1) %>% list
   #        group_split(advertiser_name) %>% 
   #        map(~{chart_maps(.x, F, mapdata, trans)}) %>% hw_grid(ncol = 3) 
```

For every ad, the Facebook ad library provides a “percentage” which relates to the share of the specific demographic that has seen the ad. So, the audience of an ad could show, for example, that 60% of the users that have seen the ad were between from Utrecht. This metric is calculated by taking the median of percentages for every unique ad. The boxplots show the median audience shares per location by advertiser.


### Google Platforms (incl. YouTube)



```{r}
  ggl_aggr %>% 
    hc_plotter(filters = dutch_parties,
           plot_type = unlist_it(trans$choices, 4),
           plot_type_sub = unlist_it(trans$targeted_ads_choices, 3),
           platform = "Google",
           trans_internal = trans,
           last_updated = update_time, minmax = "Minimum"
    )
```

For Google platforms, the Google Transparency Report provides information about the groups that the advertiser chose to target rather than just information about the audience of an ad, like Facebook does.  This information is much more insightful as it reveals the targeting strategy set by the advertisers themselves. Per [Google]((https://support.google.com/transparencyreport/answer/9575640)), targeting for election ads is limited to "[g]eographic location (except radius around a location), age, and gender." The percentages shown relate to how many of the ads were targeted towards these specific criteria.  

## Potential Reach

### Facebook Platforms (incl. Instagram) 

```{r, out.width="100%", fig.height=6, fig.width=8}


color_dat <- fb_aggr$reach %>% 
  rename(colors = color) %>% 
  filter(advertiser_name %in% dutch_parties_fb) %>% 
  distinct(advertiser_name, .keep_all = T) %>% 
  arrange(advertiser_name)

# color_dat <- set_names(color_dat$colors, color_dat$advertiser_name)

gg_reach <- fb_aggr$reach %>% 
  rename(colors = color) %>% 
  filter(advertiser_name %in% dutch_parties_fb) %>% 
  ggplot(aes(advertiser_name, potential_reach_min, color = advertiser_name)) +
  geom_boxplot() +
  scale_y_log10(labels = scales::label_number()) +
  scale_color_manual(values = unique(color_dat$colors)) +
  theme_minimal() +
  labs(y = "", x = "") +
  theme(legend.position = "none", 
        strip.background =element_rect(fill="lightgrey"), 
        strip.text = element_text(colour = 'black'), axis.title.x = element_text(size = 0.1))


gg_reach %>% 
  plotly::ggplotly(dynamicTicks = F) %>%
  plotly::layout(
    xaxis = list(automargin=TRUE),
    yaxis = list(automargin=TRUE,
                 title = "Potential Reach (Minimum)",
                 titlefont  = list(size = 0.1))
  )
```

Facebook says about this metric: 

> This is an estimate of the size of the audience that's eligible to see this ad. It's based on targeting criteria, ad placements and how many people were shown ads on Facebook apps and services in the past 30 days.

Based on that, we can assume that a higher potential reach means that a party was trying to target a broader range of citizen whereas a lower potential reach means the party was engaging in more microtargeting. The metric shown here is calculated by taking the median of potential reach for every unique ad. The boxplots show the distribution of average minimum potential reach by advertiser.